---
title: "Examples for using `theme_mengbo` when generating ggplots"
date: "`r Sys.Date()`"
author:
- name: Mengbo Li
  affiliation: Bioinformatics Division, WEHI
output:
  BiocStyle::html_document:
    toc_float: true
vignette: >
  %\VignetteIndexEntry{Examples for using `theme_mengbo` when generating ggplots}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::knitr}
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
options(width = 100, digits = 4)
knitr::opts_chunk$set(collapse = TRUE, 
                      comment = "#>", 
                      echo = TRUE, 
                      cache = FALSE, 
                      prompt = FALSE,
                      tidy = TRUE,
                      comment = NA, 
                      message = FALSE, 
                      warning = FALSE, 
                      tidy = TRUE, 
                      tidy.opts = list(width.cutoff = 60),
                      fig.width = 8, 
                      fig.height = 5, 
                      dev = "png")
```

# Overview

Here I include a few examples of using my own ggplot theme. 

```{r}
library(ggthemeML)
library(scales)
```


# Color palettes

Available color palettes so far:

```{r}
names(ggthemeML:::mengbo_palettes)
```


```{r}
show_col(mengbo_pal("main")(16))
show_col(mengbo_pal("mixed")(16))
```

# Discrete colour examples

My own ggplot theme modified based on the default ggplot theme (`theme_grey()`). Modifications include removing the minor grids, bigger axis texts, empty panel and legend background and so on. 

## Default

```{r}
mtcars2 <- within(mtcars, {
  vs <- factor(vs, labels = c("V-shaped", "Straight"))
  am <- factor(am, labels = c("Automatic", "Manual"))
  cyl  <- factor(cyl)
  gear <- factor(gear)
})

p1 <- ggplot(mtcars2) +
  geom_point(aes(x = wt, y = mpg, colour = gear)) +
  labs(
    title = "Fuel economy declines as weight increases",
    subtitle = "(1973-74)",
    caption = "Data from the 1974 Motor Trend US magazine.",
    tag = "Figure 1",
    x = "Weight (1000 lbs)",
    y = "Fuel economy (mpg)",
    colour = "Gears"
  )
```


```{r}
p1 + theme_mengbo()
p1 + facet_wrap(~ gear) +  theme_mengbo()
```

With my color palettes:

```{r}
p1 + scale_color_mengbo("mixed") + theme_mengbo()
```


## Framed figure panel

```{r}
p1 + theme_mengbo(clean_background = FALSE)
p1 + facet_wrap(~ gear) + theme_mengbo(clean_background = FALSE)
```


# Continuous color examples

```{r}
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Sepal.Length)) +
  geom_point(size = 4) +
  scale_color_mengbo("mixed", discrete = FALSE) + 
  theme_mengbo()
```




# Session information 

```{r}
sessionInfo()
```

